\section{Improvements Compared to Previous Version}

This section outlines the significant upgrades implemented in the current system version compared to the initial prototype. These improvements focus on minimizing system complexity while maximizing user engagement and retrieval efficiency.

\subsection{User Interface and Experience (UI/UX)}

\textbf{Previous Limitation:} The initial system offered a static interaction model where users could only receive text answers. There was no mechanism to interactively navigate the source video or visualize the context of the retrieved answers.

\textbf{Improvements:}
\begin{itemize}
    \item \textbf{Migration to FastAPI:} We transitioned the core backend to FastAPI. This unlocks asynchronous concurrency, allowing the system to handle multiple ingestion and retrieval requests simultaneously without blocking. It also provides automatic schema validation (via Pydantic) and auto-generated OpenAPI documentation.
    \item \textbf{Multi-Layered Caching Strategy (Redis):}
    \begin{itemize}
        \item \textbf{Query Cache:} Frequently asked questions and their answers are cached for 1 hour.
        \item \textbf{Embedding Cache:} Vector representations of repeated queries are stored to skip the inference step.
        \item \textbf{Index Cache:} The BM25 sparse index is loaded into Redis for rapid keyword lookup.
    \end{itemize}
    \item \textbf{Dynamic Video Tracking:} We have integrated a dynamic video player that automatically seeks to the exact timestamp referenced in the generated answer. This allows users to verify information instantly.
    \item \textbf{Active Frame Selection:} Users can now browse and select specific keyframes extracted from the video. Clicking a frame acts as a visual query or navigation anchor, allowing users to "jump" to relevant segments based on visual cues (e.g., a specific slide or diagram shown in the lecture).
\end{itemize}

\textbf{Impact:} These changes transform the system from a passive text-retrieval tool into an interactive multimodal learning assistant, significantly reducing the cognitive load required to cross-reference answers with lecture content. Overall they improved system stability and reduced average response latency by approximately \textbf{40\%} for non-cached queries and over \textbf{90\%} for cached queries.

\subsection{Data Pipeline Enhancements}
\textbf{Previous Limitation:} Data ingestion was a manual, single-file process. The system lacked visibility into the processing status, making it difficult to manage large course libraries.

\subsection{Optimized Embedding Strategy}

\textbf{Previous Limitation:} The prototype utilized a "brute-force" ensemble of three separate embedding models (BGE-M3, Vietnamese-embedding, and Multilingual-E5) running in parallel. While this ensured high recall, it resulted in excessive computational overhead and high latency (~3 seconds per query).

\textbf{Improvements:}
We successfully consolidated the embedding pipeline to use a single model: \textbf{Multilingual-E5-large-instruct}.

\textbf{Quantitative Analysis:}
\begin{itemize}
    \item \textbf{Latency Reduction:} By removing the overhead of running three concurrent inferences and the subsequent fusion logic, the embedding generation time dropped from $\approx$3.0s to $\approx$1.0s per query (a \textbf{66\% reduction} in latency).
    \item \textbf{Storage Efficiency:} Storing vectors from a single model rather than three reduced the storage footprint by approximately \textbf{70\%}.
    \item \textbf{Performance Maintenance:} Benchmarks on the MTEB (Massive Text Embedding Benchmark) and MIRACL datasets indicate that \textit{Multilingual-E5-large-instruct} achieves State-of-the-Art (SOTA) performance in multilingual retrieval, often matching or outperforming composite approaches for general domain queries. The instruction-tuning capability allows us to tailor the embeddings specifically for "query-passage" matching, compensating for the loss of the other two models.
\end{itemize}

\subsection{Conclusion}

The transition from a multi-model prototype to a streamlined, single-model architecture has proven that "less is more" when the right components are selected. The current system is not only faster and lighter but also far more usable due to the enhanced UI/UX features. These optimizations make the system viable for real-time deployment in an educational setting, providing students with a responsive and interactive way to query their lecture materials.